A brief study of Approximation Algorithms for 2D Packing Problem

### 2021-12-10 paper.tex
abstract modification

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  2D Packing (Strip Packing) problem is a 2-dimensional geometric optimization problem which a list of rectangles are packed into a unit-width bin with infinite height to minimize the packing height. In this paper, we study a series of approximation algorithm for 2D Packing Problem, analyze the performance. First we will study the 2 early stage intuitive approximation algorithm designed by Coffman with approximation bound 3 and 2.7. Then we will further investigate a more advanced algorithm designed by Steinberg that have a approximation bound of 2. We will also explore some future direction of this problem in the end.
\end{abstract}
\keywords{Approximation Algorithm, 2D packing, Strip Packing}

>>>>

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  2D Packing (Strip Packing) problem is a 2-dimensional geometric optimization problem which a collection of rectangles are packed into a unit-width bin while the packing height is minimized. In this paper, we study a series of approximation algorithms for 2D Packing Problem and analyze their performances. First we study two intuitive approximation algorithms designed by Coffman with approximation bounds of 3 and 2.7. We further investigate a more advanced algorithm designed by Steinberg that has an approximation bound of 2. Some future investigation directions for improving performance are given in the end.
\end{abstract}
\keywords{Approximation Algorithm, 2D packing, Strip Packing}
